Intentional stocking undermines ecological stability

### 2022-03-03 rmd/manuscript.Rmd
edit: manuscript

---
title: "Intentional stocking undermines ecological stability"
output:
  pdf_document:
    latex_engine: xelatex
#  word_document:
#    reference_docx: word_format.docx
csl: nature.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007]. Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010]. Here, contrary to this intuition, we show that stock enhancement undermines community stability with no demographic benefit to the enhanced species. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species via intensified competition. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020]. The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services. A radical change in management strategies is therefore required to achieve the sustainability of natural resources.

@@

We should prioritize habitat conservation with a broader scope of ecosystem management. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.

>>>>

---
title: "Intentional stocking undermines ecological stability"
output:
#  pdf_document:
#    latex_engine: xelatex
  word_document:
    reference_docx: word_format.docx
csl: nature.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals ("stock enhancement") [@arakiHatcheryStockingHelp2010; @krkosekDecliningWildSalmon2007]. Yet, this method is still pervasive in conservation and natural resource management, assuming that the demographic benefits exceed the associated risks [@kitadaEconomicEcologicalGenetic2018; @laikreCompromisingGeneticDiversity2010]. Here, contrary to this intuition, we show that stock enhancement undermines community stability with little demographic benefit to the enhanced species. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion while suppressing the natural recruitment of the enhanced species via intensified competition. Consistent with this prediction, stream fish communities showed greater temporal fluctuations and fewer species richness in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in Japan [@kitadaLessonsJapanMarine2020]. The current overreliance on stock enhancement may accelerate global biodiversity loss, threatening the provisioning of ecosystem services. A radical change in management strategies is therefore required to achieve the sustainability of natural resources.

@@

We should prioritize habitat conservation with a broader scope of ecosystem management to achieve the sustainability of natural resources. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
